---
title: "Download R Scripts"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The `englelab` package has a convenient function to download template R scripts for the tasks we host on our [website](http://englelab.gatech.edu/taskdownloads){target="_blank"}

```{r eval=FALSE}
englelab::get_script(type = "raw", to = "R Scripts",
                     ospan = TRUE, symspan = TRUE, rotspan = TRUE,
                     antisaccade = TRUE, va = TRUE, sact = TRUE,
                     flankerDL = TRUE, stroopDL = TRUE)
```


## `get_script()`

The first two arguments you should specify is the type of R Script you want to download and the location you want to download the R Script to (by default set to "R Scripts").

- __type__: You can download R Scripts:

    1. `type = "raw"` To create tidy raw data files from the messy E-Prime file. 
    
    2. `type = "score"` To create a scored data file from the tidy raw data file.

- __to__: Save to a folder within your project directory (i.e. "R Scripts")
    
Next, you will want to specify the tasks you want to download R Scripts for. The options are:

- __wmc__: Download the scripts for operation span, symmetry span, and rotation span. `wmc = TRUE`

- __ospan__: Download the script for operatoin span. `ospan = TRUE`

- __symspan__: Download the script for symmetry span. `symspan = TRUE`

- __rotspan__: Download the script for rotation span. `rotspan = TRUE`

- __ac__: Download the scripts for all attention control tasks `ac = TRUE`

- __antisaccade__: Download the script for the antisaccade. `antisaccade = TRUE`

- __va__: Download the script for the visual arrays. `va = TRUE`

- __sact__: Download the script for the sustained attention to cue task. `sact = TRUE`

- __flankerDL__: Download the script for the adaptive flanker deadline. `flankerDL = TRUE`

- __stroopDL__: Download the script for the adaptive stroop deadline. `stroopDL = TRUE`



