---
output: html_document
editor_options: 
  chunk_output_type: console
editor: visual
---

# STUDYNAME

1 - 2 sentence description.

## Directory Organization

------------------------------------------------------------------------

-   **data**: All data files are stored here

    -   **raw**: tidy raw data files

        -   **messy**: original raw data files, all other data files are reproducible from here

    -   **scored**: scored data files

    -   **logs**: logs on the result of data cleaning procedures

-   **documents**: Any documents related to the study and analysis procedure

-   **R**: R scripts used for processing data

-   **analyses**: Scripts and output for data analysis

-   **tasks**: Experimental programs for all the tasks used in the study

## Required Packages

------------------------------------------------------------------------

```{r}
#| eval: false

source("R/_required_packages.R")
```

## Data Preparation

------------------------------------------------------------------------

Create tidy raw data files from messy raw data files

-   **Import Directory**: data/raw/messy

-   **Output Directory**: data/raw

```{r}
source("R/1_task_raw.csv")

rm(list = ls())
```

## Data Scoring and Cleaning

------------------------------------------------------------------------

Create scored and cleaned data files from raw data files

-   **Import Directory**: data/raw

-   **Output Directory**: data/scored

-   **Data Cleaning**: A log of which subjects were removed for each task due to data cleaning can be found in data/**logs**

    \[provide a general description of some data cleaning decisions\]

-   **Reliability**: \[provide a general description of how reliability was calculated\]

```{r}
source("R/2_task_score.R")

rm(list = ls())
```

Create merged data files ready for statistical analysis from scored data files

**Import Directory**: data/scored

**Merged File**: data/**StudyName_Data.csv**

```{r}
source("R/3_merge.R")

rm(list = ls())
```

## Statistical Analysis and Data Visualization

------------------------------------------------------------------------

Perform statistical analysis and create data visualizations

Output is saved as **.html** files to **analyses/**

```{r}
library(quarto)

quarto_render("results/Analysis.qmd")

rm(list = ls())
```
